### 2010-10-17 ms/titelblatthh.tex
added some missing files for documentation
incl. heat conduction and its validation

\vspace*{-2.8cm}
\begin{minipage}[c]{.30\textwidth}
  \begin{flushleft}
   % \includegraphics[width=3cm,clip=]{LOGO/caltech_logo.eps}%
  \end{flushleft}
\end{minipage}
\begin{minipage}[c]{.43\textwidth}
\vspace*{1em}
    {GALCIT (Caltech)\\Prof. Hans G. Hornung \\ \\ Institute of Aerodynamics (TUM) \\ Prof.~Dr.-Ing. N.~A.~Adams}%
\end{minipage}
\begin{minipage}[c]{.25\textwidth}
  \begin{flushright}
    \vspace*{1em}
    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB.eps}%
  \end{flushright}
\end{minipage}

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
Simuation of a high enthalpy flow through porosities using SPH}
\end{minipage}

>>>>

\vspace*{-2.8cm}
\begin{minipage}[c]{.30\textwidth}
  \begin{flushleft}
    \includegraphics[width=3cm,clip=]{LOGO/caltech_logo}%
  \end{flushleft}
\end{minipage}
\begin{minipage}[c]{.43\textwidth}
\vspace*{1em}
    {GALCIT (Caltech)\\Prof. Hans G. Hornung \\ \\ Institute of Aerodynamics (TUM) \\ Prof.~Dr.-Ing. N.~A.~Adams}%
\end{minipage}
\begin{minipage}[c]{.25\textwidth}
  \begin{flushright}
    \vspace*{1em}
    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB}%
  \end{flushright}
\end{minipage}

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
Simuation of high enthalpy flow in porosities using SPH}
\end{minipage}
